Distributed Real-time Trajectory Replanning for Robust Motion Execution

### 2018-05-17 paper/paper.tex
paper draft2

\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,
                shadows, shapes.geometric, shapes.misc}

@@

%
%\titlerunning{Distributed Real-time Trajectory Replanning}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskin Senbaslar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskin Senbaslar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\begin{abstract}
We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, or robots breaking down.
Robots do not communicate with each other and only need to be able to sense the other robots' positions and the obstacles.
At the low-level, we use buffered voronoi cells as multi-robot collision avoidance strategy.
At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
We demonstrate our approach in simulation and on real robots, showcasing that it can operate in real-time.
%\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

\section{Introduction}
Motion planning for multi-robot systems is widely used and in particular important in cases where many robots have to interact with each other in confined spaces, potentially with many obstacles around.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
However, all such solutions assume that the resulting trajectories can be executed approximately perfectly, which is in particular not true for teams of hundreds of robots that have to operate persistently.

We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their position.
The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the correct location.
Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories.
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.

@@

Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with dynamic receding horizon.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.

@@

We consider a group of $m$ robots and each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R_i(\vp)&:\text{ physical extent of robot $i$ at position $\vp$, and}\\
    \gamma_j&: \text{ dynamic limit of robots for $j^{th}$ derivation degree}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
\end{align*}

At time $t$, each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
We assume that $\cO(t)$ is a set of $\uptheta$ convex obstacles, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap}.
However, robots cannot communicate with each other and are unaware of the other robots' trajectories.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ needs to execute a trajectory $\vf_i(t)$ such that:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i(0)}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j,\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We approximately solve this problem using a dynamic receding horizon approach.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position.
We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

@@

We now introduce important mathematical concepts and notation.

\subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_i\leq 0 \right\} \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of vector $\vp$.

@@

The set of all buffered voronoi cells is called the buffered voronoi decomposition of the space.
For a given buffered voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside one of the buffered voronoi cells at most.
We use this property in order to avoid robot-to-robot collisions.

Using the hyperspaces $\cS_i^j$ we can reformulate $\cV_i$:
\begin{equation}
    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \text{ , where } \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}.
    \label{voronoiEquation}
\end{equation}

@@

Thus, we can compute the buffered voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.

@@

The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve.
A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein}.
%This is called the \emph{convex hull property of B\'ezier curves}.
We use this property to avoid robot-to-obstacle collisions.

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at iteration $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece, $\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory, and $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $t\in[0, T^{K}_{i,j}]$, $j \in \{1,2,\ldots,l\}$ and $\rho \in \{0,1,\ldots,d\}$.

@@

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative.
A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
We take the vector difference of those values and require it to be equal to $\vzero$.
A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
The construction of the QP is discussed in previous work~\cite{crazyplanning-ieeetro}.

@@

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$ and at each iteration $K$ we compute a trajectory $f^K_i(t)$.
The planning horizon $\tau'$ is automatically adjusted, but a user can provide the desired planning horizon $\tau$.
In the following, we assume that the robots are spherical with a uniform radius $r_s$.
%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot, see Fig.~\ref{fig:flowchart}.
In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
We use this discrete path as an initial guess in trajectory optimization.
If discrete planning is not required, we use the control points of the previous plan as the initial guess.

We construct a QP with hard constraints for trajectory optimization in a slightly different way, depending if discrete planning was executed or not.
In both cases, buffered voronoi cells are used to ensure collision-free operation for up to $\delta t$ and collisions with static obstacles are avoided for the planning horizon.

Dynamic limits cannot be represented as linear constraints in our QP.
Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving the QP.

At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.

@@

In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered voronoi cell $\cV_i(\psi)$.
We also assume that we have a current representation of the occupied space ($\cO(\psi)$), which can be achieved in practice by using LIDAR or RGB-D sensors.

Robot $i$ executes discrete planning if any of the following conditions is true:
\begin{enumerate}
    \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(t)) \cap \cO(\psi) \neq \emptyset$,
    \item The first piece of the previously planned trajectory is outside the robot's buffered voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i(\psi)$, or
    \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K-1}_i(t)) \cap \cO(\psi) \neq \emptyset$.
\end{enumerate}
The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear, and the third condition handles numeric issues and dynamic obstacles.

Discrete planning uses a dynamic receding horizon approach. First, we find the earliest time $\tau'\in [\min(\tau, T_i-\psi), T_i-\psi]$ where the original trajectory is collision-free with respect to both obstacles and other robots.
Second, we use a discrete graph search to find a path from the robots current location to $\vo_i(\psi+\tau')$ that avoids both static obstacles and other robots.
If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage.
Third, we use the first $l$ segments of the discrete path to uniformly place the new estimated control points on top of those segments.
In case the discrete path has fewer than $l$ segments, the last discrete segment is shared between multiple B\'ezier curves.
Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at location $\vo_i(\psi+\tau')$ if we would follow the discrete path with constant speed.
However, to guarantee collision-free operation, we ensure that $T_{i,1}^K\geq \delta t$ in any case.

@@

The first term of the objective is the combination of integrated squared derivatives with weights $\lambda_e$ \cite{crazyplanning-ieeetro,richterISRR}.
The second term of the objective penalizes deviation from given end points for each piece of the trajectory with different weights $\theta_j$.
In case discrete planning is performed, we attempt to keep the position of the last guessed control point, i.e., we set $\theta_l$ to a positive value,  $\vchi_l = P^K_{i,l,d}$, and $\theta_j = 0, \forall j < l$.
If discrete planning is not performed, we attempt to stay as close as possible to the original trajectory, i.e.,  we set $\theta_1 = 0$, and $\theta_j, \forall j \geq 2$ to positive values (increasing with $j$) and $\vchi_j = \vo_i(\psi + \sum_{u=1}^j T^{K}_{i,u})$.
%If discrete planning is not performed, we require end points of each piece to get closer to the robot's position at corresponding times if it had followed the original trajectory, weighing each piece more than the previous one.
This is an approximation we make for the cost function defined in \eqref{eq:problem:opt}.
Matrix $H$ (see Section~\ref{trajectoryOptimization}) can be constructed for the first term of our objective~\cite{crazyplanning-ieeetro}.
%The construction of matrix $H$, as defined in Section~\ref{trajectoryOptimization}, for the first term of our objective function is explained in \cite{crazyplanning-ieeetro}.
The second term is a quadratic function of the control points; hence it is straightforward to construct the $H$ matrix and the $\vg$ vector.

For robot-to-robot collision avoidance, the buffered voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
% . For each control point of the first piece, we add $m-1$ hyperspace constraints as
% \begin{align}
%     \alpha_i^j \cdot \vP^{K}_{i,1,\rho} \leq \beta_i^j, \rho \in \{0,1,...,d\}, j \in \{1,2,...,m\}\setminus\{i\}.
% \end{align}
These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.

For robot-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO(\psi)$ for each curve piece $j$.
Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$ that can, for example, be computed using support vector machines~\cite{SVM}.
We shift each hyperplane towards its obstacle and than shift it back using the radius $r_s$ to account for the physical extent of the robot.
We add hyperspace constraints as before requiring control points of the $j^{th}$ piece in the non-occupied side of each hyperplane $M_j^b$
These constraints ensure that no robot-to-obstacle constraint will occur up to time $\tau'$.
In case discrete planning was executed, we additionally treat other robots as static obstacles.
Fig.~\ref{fig:swap2_2} (b) shows the effective set of hyperspaces for a $l=4$ trajectory.

Moreover, we add continuity constraints that enforces continuity requirement between pieces and initial point constraints.

All constraints are linear and the constraint matrix $A$ and its bounds can be constructed as explained in Section~\ref{trajectoryOptimization}.
The number of decision variables in our QP is $l(d+1)n$.
Let $\uptheta'$ describe the number of considered static obstacles, i.e., $\uptheta'$ is equal to $\uptheta + (m-1)$ if discrete planning was performed and $\uptheta$ otherwise.
We add $(m-1)(d+1) + \uptheta' l(d+1) + (c+1)nl$ linear constraints, where the terms refer to the voronoi hyperspace, obstacle hyperspace, and continuity constraints, respectively.
For our example in Fig.~\ref{fig:swap2_2}, we have $n=2$, $m=2$, $d=7$, $l=4$, and $c=2$. Thus, we have 64 decision variables and $8 + 128 + 24$ linear constraints.

@@

\subsection{Theoretical Guarantees} %maybe
To provide formal guarantees, we make the following assumptions:
First, the robots have first-order integrator dynamics (and thus $c=0$);
second, the execution of the robots in synchronous;
third, robots execute trajectories perfectly;
fourth, robot trajectories are initially valid up to time $\tau$; and
fifth, obstacles are static.

>>>>

\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,
                shadows, shapes.geometric, shapes.misc}
\usepackage[utf8]{inputenc}

\inputencoding{utf8}

@@

%
%\titlerunning{Distributed Real-time Trajectory Replanning}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskın Şenbaşlar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskın Şenbaşlar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\begin{abstract}
We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
At the low-level, we use buffered Voronoi cells as multi-robot collision avoidance strategy.
At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
We demonstrate our approach in simulation and on real robots, showing that it can operate in real-time.
%\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

\section{Introduction}
Motion planning for multi-robot systems is widely used and in particular important in cases where many robots have to interact with each other in confined spaces, potentially with many obstacles around.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
All such solutions assume that the resulting trajectories can be executed approximately perfectly, which is not true for teams of hundreds of robots that have to operate persistently.

We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, robots breaking down, or external disturbances.
Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their positions.
The pre-planned trajectories are collision-free, but neither considers the new obstacle nor that the fact that blue robot does not start at its correct location.
Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories.
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and the obstacles around them.

@@

Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with a dynamic receding horizon approach.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.

@@

We consider a group of $m$ robots and each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R_i(\vp)&:\text{ physical extent of robot $i$ at position $\vp$, and}\\
    \gamma_j&: \text{ dynamic limit of the robot for $j^{th}$ derivation degree}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
\end{align*}

At time $t$, each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
We assume that $\cO(t)$ is a set of $\uptheta$ convex obstacles, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap}.
Robots cannot communicate with each other and are unaware of the other robots' trajectories.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ needs to execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j\text{ for all desired $j$s},\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We approximately solve this problem iteratively using a dynamic receding horizon approach.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to period $\delta t$.
%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

@@

We now introduce important mathematical concepts and notations we use.

\subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_i\leq 0 \right\} \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of vector $\vp$.

@@

% The set of all buffered Voronoi cells is called the buffered Voronoi decomposition of the space.
For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside at most one of the buffered Voronoi cells.
We use this property in order to avoid robot-to-robot collisions.

Using the hyperspaces $\cS_i^j$ we can reformulate $\cV_i$ as follows:
\begin{equation}
    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \text{ , where } \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}.
    \label{voronoiEquation}
\end{equation}

@@

Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.

@@

The curve starts at $\vP_0$ and ends at $\vP_d$, however does not interpolate other control points.
A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein}.
%This is called the \emph{convex hull property of B\'ezier curves}.
We use this property to avoid robot-to-obstacle collisions.

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece where $j \in \{1,2,\ldots,l\}$. $\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$. $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $\rho \in \{0,1,\ldots,d\}$.

@@

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative. This translates to $n$ linear constraints on control points, $n$ being the dimension we are working in.
A continuity constraint between curve $j$ and curve $j+1$ requires the end of curve $j$ to be equal to the beginning of curve $j+1$ at any order of differentiation.
We take the vector difference of those values and require it to be equal to $\vzero$. This translates to $n$ linear constraints on control points.
A hyperspace constraint requires all control points of a curve to be on a specific side of a hyperplane. If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points. All 3 types of constraints are linear in control points, and the exact construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.

@@

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$ and at each iteration $K$ we compute a trajectory $f^K_i(t)$.
The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.
In the following, we assume that the robots are spherical with a uniform radius $r_s$.
%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot, see Fig.~\ref{fig:flowchart}.
%In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
%If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
%We use this discrete path as an initial guess in trajectory optimization.
%If discrete planning is not required, we use the control points of the previous plan as the initial guess.

%We construct a QP with hard constraints for trajectory optimization in a slightly different way depending on whether discrete planning was executed or not.
%In both cases, buffered Voronoi cells are used to ensure collision-free operation for up to time $\delta t$ and collisions with static obstacles are avoided for the planning horizon.

%Dynamic limits cannot be represented as linear constraints in our QP.
%Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
%As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving of the QP.

%At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration. We execute this trajectory for a period of $\delta t$ and replan for the next iteration.

@@

In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i(\psi)$.
We also assume that we have a current representation of the occupied space ($\cO(\psi)$), which can be achieved in practice by using LIDAR or RGB-D sensors.

Robot $i$ executes discrete planning if any of the following conditions are true:
\begin{enumerate}
    \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(t)) \cap \cO(\psi) \neq \emptyset$,
    \item The first piece of the previously planned trajectory is outside the robot's buffered Voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i(\psi)$, or
    \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K-1}_i(t)) \cap \cO(\psi) \neq \emptyset$.
\end{enumerate}
The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear and robots move towards each other a lot, and the third condition handles numeric issues and dynamic obstacles.

Discrete planning uses a dynamic receding horizon approach. First, we find the earliest time $\tau'\in [\min(\tau, T_i-\psi), T_i-\psi]$ where the original trajectory is collision-free at time $\psi + \tau'$ with respect to both obstacles and other robots.
Second, we use a discrete graph search to find a path from the robots current location to $\vo_i(\psi+\tau')$ that avoids both static obstacles and other robots.
If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage and construct QP as if discrete planning was not required.
Third, we use the first $l$ segments of the discrete path to uniformly place the new estimated control points on top of those segments.
In case the discrete path has fewer than $l$ segments, the last discrete segment is shared between multiple B\'ezier curves.
Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at $\vo_i(\psi+\tau')$ if we followed the discrete path with constant speed.
To guarantee collision-free operation, we ensure that $T_{i,1}^K\geq \delta t$ in any case.

@@

The first term of the objective is the combination of integrated squared derivatives up to degree $\cE$ with weights $\lambda_e$ \cite{crazyplanning-ieeetro}. It minimizes the energy through curve. %richterISRR
The second term of the objective penalizes deviation from given end points for each piece of the trajectory with different weights $\theta_j$.
In case discrete planning is performed, we attempt to get to the position of the last guessed control point, i.e., we set $\theta_l$ to a positive value, enforcing $\vP^K_{i,l,d} = \vchi_l$, and $\theta_j = 0, \forall j < l$.
If discrete planning is not performed, we attempt to stay as close as possible to the original trajectory, i.e.,  we set $\theta_1 = 0$, and $\theta_j, \forall j \geq 2$ to positive values (increasing with $j$) and $\vchi_j = \vo_i(\psi + \sum_{u=1}^j T^{K}_{i,u})$.
%If discrete planning is not performed, we require end points of each piece to get closer to the robot's position at corresponding times if it had followed the original trajectory, weighing each piece more than the previous one.
%This is an approximation we make for the cost function defined in \eqref{eq:problem:opt}.
Matrix $H$ (see Section~\ref{trajectoryOptimization}) can be constructed for the first term of our objective~\cite{crazyplanning-ieeetro}.
%The construction of matrix $H$, as defined in Section~\ref{trajectoryOptimization}, for the first term of our objective function is explained in \cite{crazyplanning-ieeetro}.
The second term is a quadratic function of the control points; hence it is straightforward to construct the $H$ matrix and the $\vg$ vector.

For robot-to-robot collision avoidance, the buffered Voronoi hyperplanes are computed according to \eqref{voronoiAlphaBeta} and $m-1$ hyperspace constraints are added for the first piece.
% . For each control point of the first piece, we add $m-1$ hyperspace constraints as
% \begin{align}
%     \alpha_i^j \cdot \vP^{K}_{i,1,\rho} \leq \beta_i^j, \rho \in \{0,1,...,d\}, j \in \{1,2,...,m\}\setminus\{i\}.
% \end{align}
These constraints ensure that the first piece stays inside $\cV_i$ because of the convexity of $\cV_i$ and the convex hull property of B\'ezier curves.
As long as $T^{K}_{i,1} \geq \delta t$ and all other robots stay inside their Voronoi cells up to time $\delta t$, we can be sure that no robot-to-robot collision will occur up to time $\delta t$.

For robot-obstacle collision avoidance we compute separating hyperplanes between convex obstacles $\cO(\psi)$ for each curve piece $j$.
Let $M_j^b$ be the separating hyperplane between the initially guessed control points of the $j^{th}$ piece from the $b^{th}$ obstacle obtained from $\cO(\psi)$. That can, for example, be computed using support vector machines~\cite{SVM}.
We shift each hyperplane towards its obstacle and than shift it back using the radius $r_s$ to account for the physical extent of the robot.
We add hyperspace constraints as before requiring control points of the $j^{th}$ piece in the non-occupied side of each hyperplane $M_j^b$
These constraints ensure that no robot-to-obstacle constraint will occur up to time $\tau'$.
In case discrete planning was executed, we additionally treat other robots as static obstacles.
Fig.~\ref{fig:swap2_2} (b) shows the effective set of hyperspaces for our example.

Moreover, we add continuity constraints that enforce continuity requirement between pieces. Then, we add initial point constraints that enforce continuity requirements in the beginning that ensures continuity between iterations.

All constraints are linear and matrix $A$ and its bounds can be constructed as explained in Section~\ref{trajectoryOptimization}.
The number of decision variables in our QP is $l(d+1)n$.
Let $\uptheta'$ describe the number of considered static obstacles, i.e., $\uptheta'$ is equal to $\uptheta + (m-1)$ if discrete planning was performed and $\uptheta$ otherwise.
We add $(m-1)(d+1) + \uptheta' l(d+1) + (c+1)nl$ linear constraints, where the terms refer to the Voronoi hyperspace, obstacle hyperspace, and continuity constraints, respectively.
For our example in Fig.~\ref{fig:swap2_2}, we have $n=2$, $m=2$, $d=7$, $l=4$, and $c=2$. Thus, we have 64 decision variables and $8 + 128 + 24 = 160$ linear constraints.

@@

\subsection{Theoretical Guarantees} %maybe

For robot-robot collision avoidance our approach uses buffered Voronois cells and retains the same theoretical guarantee, that we first restate here:
If robots start in a collision free configuration (that is, $\|\vp_i - \vp_j\| \geq 2r_s, \forall i\neq j$), then all future configurations are collision-free.

However, this has only been proven in the case of synchronous robot execution, if robots have first-order integrator dynamics ($c=0$), and if they execute their trajectories perfectly~\cite{bufferedVoronoiCells}.
We cannot provide formal guarantees under arbitrary disturbances.
However, our QP formulation allows us to easily detect failure cases because we model all safety-critical parts as hard constraints.
